Post-doc project: A complex food-web theory of stability against perturbation

### 2022-11-18 report/project_definition.Rmd
Clarify differences between McCann and Brose

The question at 1bn pound is "what is driving stability?", i.e. the propagation
of perturbations across food-webs. Early studies focused on the effect of
removing one species either by looking at the topology [e.g.,
@dunne_network_2002] or dynamic [@stouffer_compartmentalization_2011]. In that
sense, it would be interesting to see if environmental stochasticity predicts the same
pattern that species extinction (i.e. pertubation for one species only).

The big other ingredient of food-web stability is the strength of species
interactions. The tremendous early work of McCann and other authors about the
distribution of interaction strength is really interesting, showing that
coupling weak interactions to strong one stabilize food-web dynamics.
Interestingly, I see two schools on the definition of interaction strengths in
the Bioenergetic model. McCann defines it by modulating consumer preference
($\omega$) such as $I_{ki} = \omega_{ik}* x_i * y_i / B_{0i}$ while
@brose_allometric_2006 modules interaction strength by modulating predator/prey
mass ratios (Z) such as Z increases the metabolism of predators decreases
relative to prey (i.e. $x_i$ and $y_i$). Thus increasing Z decreases $I_{ki}$.
The main difference between Brose and McCann approaches is that the Brose
approach of modulating interactions also modulates metabolic losses ($x_iy_iB_i$).
Then the approach of McCann has the advantage to only change feeding rates but
it is rather phenomenological modelling while Brose approach is more mechanistic
(fully metabolic) but it changes two things at the same time.

@@

@@

>>>>

The question at 1bn pounds is "what is driving stability?", i.e. the propagation
of perturbations across food-webs. Early studies focused on the effect of
removing one species either by looking at the topology [e.g.,
@dunne_network_2002] or dynamic [@stouffer_compartmentalization_2011]. In that
sense, it would be interesting to see if environmental stochasticity predicts the same
pattern that species extinction (i.e. pertubation for one species only).

The big other ingredient of food-web stability is the strength of species
interactions, as demonstrated by previous studies [@mccann_weak_1998;
@brose_allometric_2006]. @mccann_weak_1998 showed that food-web having strong
interactions can persist if the strong interactions are coupled with weak ones.
Interestingly, a strong interaction needs to be coupled in two ways, by a
feeding and a competitive interactions. @brose_allometric_2006 showed the
strength of interactions are driven by body size, such larger body sized animals
produce lower interaction strengths (because of their lower metabolic rates).

Interestingly, I see two schools on the definition of interaction strengths in
the Bioenergetic model. McCann defines it by modulating consumer preference
($\omega$) such as $I_{ki} = \omega_{ik}* x_i * y_i / B_{0i}$ while
@brose_allometric_2006 modules interaction strength by modulating predator/prey
mass ratios (Z) such as Z decrease the metabolism of predators
relative to prey (i.e. $x_i$ and $y_i$). Thus increasing Z decreases $I_{ki}$.
A common feature of both approaches is that they both consider that the strength
of interactions decrease as the trophic level increases.

A main difference between Brose and McCann approaches is that the Brose
approach of modulating interactions also modulates metabolic losses ($x_iy_iB_i$).
Then the approach of McCann has the advantage to only change feeding rates but
it is rather phenomenological modelling while Brose approach is more mechanistic
(fully metabolic) but it changes two things at the same time.

Although in complex food-webs, Brose method can create strong asymetry in
interaction strength by coupling specialists and generalists, as they
respectively generate strong and weak interactions. Such mechanism is
triggered by the fact that consumer preference is equally shared among preys
($\omega_ki = 1 \ \sum_k 1 $, such as $\omega_{ki} = 1$ or .1 for a consumer
having one prey or 10 preys).

@@

## Stochasticity in food-webs

@vasseur_environmental_2007 found that Stochasticity and response diversity can
stabilize food-web in a McCann model with strong asymetry in species interactions.
Is it valid also with a Brose model without this asymetry? Is it also valid with
different functional responses?

@@

## Response diversity
